STAT0017 ICA 1 2018-19

### 2019-03-22 STAT0017_ICA1/SN17052480.Rmd
little change
finished the exploratory

```{r, include = FALSE}
# Load the data (you will need to edit this to point to the correct directory
# on your computer)
setwd("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1")
raw_wm <- load("wm.Rdata")
raw_pot <- load("pot.Rdata")
# You will also need to load any R libraries that you want to use.
library("evd")
library("evdbayes")
library("ismev")
library("revdbayes")
library("threshr")
library("bayesplot")
library("coda")
source("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pjnfunctions.R")
# Some parts of the analyses are based on simulation.
# We set a set a random number seed so that
# 1. The numeric results on which you comments will not change each time you run
#    your code (unless you change the order of the analyses)
# 2. Your work is easier for me to mark.
#### PLEASE DO NOT CHANGE THE FOLLOWING LINE OF CODE (KEEP THE SEED as 17) ####
set.seed(17)
```

@@

```{r}
# Add R code here (and similarly elsewhere)
```

@@

## Build a GEV regression model
test123
${}$\hspace*{\fill} [15]

>>>>

```{r, include = FALSE}
# Load the data (you will need to edit this to point to the correct directory
# on your computer)
setwd("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1")
load("wm.Rdata")
load("pot.Rdata")
# You will also need to load any R libraries that you want to use.
library("evd")
library("evdbayes")
library("ismev")
library("revdbayes")
library("threshr")
library("bayesplot")
library("coda")
source("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pjnfunctions.R")
# Some parts of the analyses are based on simulation.
# We set a set a random number seed so that
# 1. The numeric results on which you comments will not change each time you run
#    your code (unless you change the order of the analyses)
# 2. Your work is easier for me to mark.
#### PLEASE DO NOT CHANGE THE FOLLOWING LINE OF CODE (KEEP THE SEED as 17) ####
set.seed(17)
```

@@

```{r}
# Add R code here (and similarly elsewhere)
plot(wm$waterYear,wm$Hs,bty="l",pch=20,xlab="year",ylab="wave height (in metres)")
#(wm$Hs~wm$meanNAO) 
plot(wm$meanNAO,wm$Hs,bty="l",pch=20,xlab="year",ylab="the mean of NAO")
abline(lm(wm$Hs~wm$meanNAO), col="red") # regression line (wm$Hs~wm$meanNAO) 
lines(lowess(wm$Hs~wm$meanNAO), col="blue") # lowess line (wm$Hs~wm$meanNAO)
#(wm$Hs~wm$maxNAO)
plot(wm$maxNAO,wm$Hs,bty="l",pch=20,xlab="year",ylab="the max of NAO")
abline(lm(wm$Hs~wm$maxNAO), col="red") # regression line (wm$Hs~wm$maxNAO)
lines(lowess(wm$Hs~wm$maxNAO), col="blue") # lowess line (wm$Hs~wm$maxNAO)
#(wm$Hs~wm$meanA0)
plot(wm$meanA0,wm$Hs,bty="l",pch=20,xlab="year",ylab="the mean of AO")
abline(lm(wm$Hs~wm$meanA0), col="red") # regression line (wm$Hs~wm$meanA0)
lines(lowess(wm$Hs~wm$meanA0), col="blue") # lowess line (wm$Hs~wm$meanA0)
#(wm$Hs~wm$maxAO)
plot(wm$maxAO,wm$Hs,bty="l",pch=20,xlab="year",ylab="the max of AO")
abline(lm(wm$Hs~wm$maxAO), col="red") # regression line (wm$Hs~wm$maxAO)
lines(lowess(wm$Hs~wm$maxAO), col="blue") # lowess line (wm$Hs~wm$maxAO)

```

@@

## Build a GEV regression model
